Data preparation

### 2023-09-25 procesamiento/prod_prep-macro.Rmd
modelos chao

```{r merge}
df1$ccode <- as.numeric(df1$country)
df2 <- 
df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","gini","gv_spen","palmawd","rgdpna","pc10_2017","pc50_2017")],by = "ccode")

df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")
df2 <- df2 %>% rename(country3=c3)
df2 <- df2 %>% select(country,country2, country3, everything())
```

>>>>

```{r merge}
df1$ccode <- as.numeric(df1$country)
df2 <- 
df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","gini","gv_spen","palmawd","rgdpna","pc10_2017","pc50_2017","individualism","gdp")],by = "ccode")
df2$ratio10_50 <- df2$pc10_2017/df2$pc50_2017
df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")
df2 <- df2 %>% rename(country3=c3)
df2 <- df2 %>% select(country,country2, country3, everything())
```
